---
title: "Anesthesia Gas MUE"
author: "Brian Gulbis"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(forcats)
library(themebg)
library(kableExtra)

dirr::get_rds("../data/tidy")
```

```{r, fig.cap="Type of gas used by category "}
data_gas %>%
    left_join(data_surgeries, by = c("millennium.id", "surg.start.datetime")) %>%
    filter(!is.na(surg.type)) %>%
    mutate_at("surg.type", factor, levels = data_surgery_types$surg.type) %>%
    mutate_at("surg.type", fct_rev) %>%
    ggplot(aes(x = surg.type, fill = gas)) +
    geom_bar() +
    xlab("Surgery Category") +
    ylab("Patients") +
    scale_fill_brewer("Gas Used", palette = "Dark2") +
    coord_flip() +
    theme_bg(yticks = FALSE) +
    theme(legend.title = element_text(color = "grey35"))
```

```{r, fig.cap="Distribution of surgery duration by type of gas used"}
data_gas %>%
    left_join(data_surgeries, by = c("millennium.id", "surg.start.datetime")) %>%
    filter(!is.na(surgery_duration)) %>%
    mutate_at("surgery_duration", as.numeric) %>%
    ggplot(aes(x = gas, y = surgery_duration)) +
    geom_boxplot() +
    xlab("Gas Used") +
    ylab("Surgery Duration (hours)") +
    theme_bg()
```

```{r}
totals_gas <- data_gas %>%
    ungroup() %>%
    count(gas) %>%
    rename(total = n)

data_gas %>%
    left_join(data_patients, by = "millennium.id") %>%
    group_by(gas) %>%
    summarize_at(c("obesity", "osa"), sum, na.rm = TRUE) %>%
    left_join(totals_gas, by = "gas") %>%
    mutate_at(c("obesity", "osa"), funs(. / total * 100))
```

Turn down flow rate after induction
How many have sevo flow rate < 2
Plot time course of flow rates
Duration of case by gas

```{r}
data_gas_intervals %>%
    filter(flow_avg > 0) %>%
    ggplot(aes(x = time_group, y = flow_avg, color = gas)) +
    geom_smooth()
```

```{r}
gas_real_cost %>%
    ggplot(aes(x = run_time, y = flow, color = gas)) +
    geom_smooth()
```

```{r}
gas_real_cost %>%
    ggplot(aes(x = run_time, y = fresh_gas, color = gas)) +
    geom_smooth()
```

```{r}
data_surgeries %>%
    left_join(data_gas, by = c("millennium.id", "surg.start.datetime")) %>%
    count(surgery, gas, sort = TRUE)
```

```{r}
data_patients %>%
    summarize_at(c("obesity", "osa"), sum, na.rm = TRUE)
```

```{r}
data_surgeries %>%
    left_join(data_gas, by = c("millennium.id", "surg.start.datetime")) %>%
    filter(!is.na(gas)) %>%
    ggplot(aes(x = gas, y = surgery_duration)) +
    geom_boxplot()
```

